biclaR

### 2025-02-13 code/biclarwww/index.Rmd
auxiliar files for render www

---
title: "biclaR"
output:
  html_document:
    theme:
      bg: "#FFFFFF"
      fg: "#000000"
      highlight: "#000000"
      primary: "#000000"
      base_font:
        google: "Lexend" #Prompt
      code_font:
        google: "JetBrains Mono"
    css: css/style.css
    includes:
      after_body: img/footer.html
---

>>>>

---
title: "biclaR"
output:
  html_document:
    theme:
      bg: "#FFFFFF"
      fg: "#000000"
      highlight: "#000000"
      primary: "#000000"
      base_font:
        google: "Lexend" #Prompt
      code_font:
        google: "JetBrains Mono"
    css: css/style.css
    includes:
      after_body: img/footer.html
    # self_contained: false
---
